Conditional selectivity for triplestores

### 2012-09-06 conditional/trunk/selectivity-basic.tex
related work stub
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@358 43ef1190-90fd-4dd7-a769-d0121f02b80e

\title{Conditional selectivity for Hexastores}

@@

\begin{abstract}
  This paper explores selectivity estimation for single triple
  patterns in SPARQL queries. In this paper we see how the common
  assumption of independence of the selectivity of RDF terms can be
  abandoned. We shall also find it instructive to explore how
  selectivity can be determined exactly when a SPARQL query is
  executed on a Hexastore triple store
  \cite{Weiss:2008:HSI:1453856.1453965}. Finally, we will suggest
  further directions for selectivity estimation in the conditional
  regime.

@@

>>>>

\title{Conditional selectivity for triplestores}

@@

\begin{abstract}
  This paper explores selectivity estimation for single triple
  patterns in SPARQL queries. In this paper we see how the common
  assumption of independence of the selectivity of RDF terms can be
  abandoned. We proceed to extend SPLENDID\cite{splendid} using the
  new formalism and demonstrate how the VoID data descriptions can be
  further exploited in the conditional regime. Finally, we will
  explore how selectivity can be determined exactly when a SPARQL
  query is executed on a fully indexed triplestore, such as
  Hexastore\cite{Weiss:2008:HSI:1453856.1453965}. Finally, we will
  suggest further directions for selectivity estimation in the
  conditional regime.

@@

\section{Related Work}

\cite{splendid}, \cite{wodqa} \todo{write this}.
